A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-21 latex/main.tex
Updates from Shing

\item The ARG in tskit format has been deposited at Zenodo and is publicly
available at \url{https://zenodo.org/records/17558489}. The UShER tree
in tskit format is also available, as well as the intersection files.
\item The sequences alignments in VCF Zarr format have been deposited at 
Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The complete configuration file for running sc2ts to build the ARG above is 
publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly 
available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original code of sc2ts is publicly available on 
GitHub at \url{https://github.com/jeromekelleher/sc2ts/}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
% Methods dev, software dev, and approaches
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
% Data analysis and literature review/synthesis
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, everyone;
funding acquisition, JK;
resources, JK;
supervision, JK.

@@

% TODO: https://github.com/jeromekelleher/sc2ts-paper/issues/922
The authors declare no competing interests.

@@

% TODO implement this 
% When we compare the intersection of the base sc2ts ARG
% (pre site-remapping), sc2ts is very slightly more parsimonious
% % TODO: https://github.com/jeromekelleher/sc2ts-paper/issues/684
% with XX mutations over the YYY sites shared between them.
After site remapping, and including all mutations involving
deletion characters, sc2ts has 143,690 mutations more
(2,078,370 vs 1,934,680). If we exclude mutations involving
deletions in sc2ts, this is reduced to 46,371 more (2.3\%) than UShER.
If we restrict to the 26,192 sites that were not remapped,
sc2ts has 4,785 (0.26\%) fewer mutations than UShER,
and has around 2.5 times more mutations than UShER
on the 163 sites that were post-hoc remapped.

>>>>

\item The ARG in tskit format has been deposited at Zenodo and is publicly
available at \url{https://zenodo.org/records/17558489}. The UShER tree
in tskit format is also available, as well as the intersection files.
\item The sequences alignments in VCF Zarr format have been deposited at 
Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The complete configuration file for running sc2ts to build the ARG above is 
publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly 
available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original code of sc2ts is publicly available on 
GitHub at \url{https://github.com/tskit-dev/sc2ts}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
% Methodology, software, resources, visualization
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
% Invesigation, data curation, formal analysis, validation
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, everyone;
resources, JK;
supervision, JK;
funding acquisition, JK.

@@

% https://github.com/jeromekelleher/sc2ts-paper/issues/922
The authors declare no competing interests.

@@

% TODO implement this 
% When we compare the intersection of the base sc2ts ARG
% (pre site-remapping), sc2ts is very slightly more parsimonious
% See https://github.com/jeromekelleher/sc2ts-paper/issues/684
% with XX mutations over the YYY sites shared between them.
After site remapping, and including all mutations involving
deletion characters, sc2ts has 143,690 mutations more
(2,078,370 vs 1,934,680). If we exclude mutations involving
deletions in sc2ts, this is reduced to 46,371 more (2.3\%) than UShER.
If we restrict to the 26,192 sites that were not remapped,
sc2ts has 4,785 (0.26\%) fewer mutations than UShER,
and has around 2.5 times more mutations than UShER
on the 163 sites that were post-hoc remapped.
